Kolmogorov-Smirnov

### 2020-04-09 ks/ks.Rmd
Use percentages in fig 1

---
title: "Kolmogorov-Smirnov"
output: html_document
---

@@

```{r}
library(testthat)
library(ggplot2)
```

@@

Create table:

@@

@@

```{r}
knitr::kable(df)
```

@@

```{r}
write.csv(df, "table_1.csv", row.names = FALSE)
```

@@

```{r}
ggplot(df, aes(x = haplotype, y = f, fill = proteome)) + 
  scale_fill_manual(values = c("human" = "#ffffff", "covid" = "#cccccc")) +
  geom_col(position = position_dodge(), color = "#000000") + xlab("HLA haplotype") + 
  ylab("% epitopes overlapping \nwith transmembrane helix") +
  geom_hline(yintercept = mean(f_human), lty = "dashed") +
  geom_hline(yintercept = mean(f_covid), lty = "dotted") +
  labs(
    caption = paste0(
      "Dashed line: average in humans: ", formatC(mean(f_human), digits = 2),". ",
      "Dotted line: average in COVID-19: ", formatC(mean(f_covid), digits = 2),"."  
    )
  ) + ggsave("fig_1.png", width = 7, height = 7)
```

>>>>

---
title: "Kolmogorov-Smirnov"
author: Richel J.C. Bilderbeek
output: pdf_document
---

@@

```{r, message=FALSE}
library(testthat)
library(tidyr)
library(ggplot2)
```

@@

Create tidy table:

@@

Create wide (untidy) table:

```{r}
df_wide <- spread(df, proteome, f)
```

@@

```{r}
knitr::kable(df_wide, caption = "Fraction of epitopes overlapping with transmembrane helix")
```

@@

```{r}
write.csv(df_wide, "table_1.csv", row.names = FALSE)
```

@@

```{r}
ggplot(df, aes(x = haplotype, y = f, fill = proteome)) + 
  scale_fill_manual(values = c("human" = "#ffffff", "covid" = "#cccccc")) +
  geom_col(position = position_dodge(), color = "#000000") + xlab("HLA haplotype") + 
  ylab("Epitopes overlapping \nwith transmembrane helix") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 3)) +
  geom_hline(yintercept = mean(f_human), lty = "dashed") +
  geom_hline(yintercept = mean(f_covid), lty = "dotted") +
  labs(
    caption = paste0(
      "Dashed line: average in humans: ", formatC(100.0 * mean(f_human), digits = 2),"%. ",
      "Dotted line: average in COVID-19: ", formatC(100.0 * mean(f_covid), digits = 2),"%."  
    )
  ) + ggsave("fig_1.png", width = 7, height = 7)
```
